\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
%\usepackage{lipsum}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\fancyfoot[R]{
  \quad \hrule \quad \\
  \textsf{Eric Geiger - Curriculum Vitae \hfill \thepage}
}

\setlength\parindent{0pt}

% Add courses prepared to teach section

\begin{document}
\textsf{\textbf{\LARGE Eric Geiger}}
% Last updated: 9/25/2020 

\bigskip

Department of Mathematics \hfill Cell: (919) 434-7608 

Yale University \hfill E-mail: eric.geiger@yale.edu

442 Dunham Lab \hfill Website: https://egeig.com 

10 Hillhouse Ave

New Haven, CT 06511


%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip
\bigskip

\textsf{\textbf{\Large Education} \hrulefill}

\medskip
Ph.D., Mathematics, North Carolina State University \hfill  2021

Advisor: Irina Kogan

\medskip
 M.S., Mathematics, North Carolina State University  \hfill 2018

\medskip
B.S., Mathematics, University of North Carolina at Chapel Hill \hfill 2014

Minor in Religious Studies
        
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Professional Appointments} \hrulefill}

\medskip
Yale University, Lecturer  \hfill Fall 2021 - Spring 2023

%
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Publications and Preprints} \hrulefill}

\medskip
E. Geiger, I. A. Kogan, 

Non-congruent non-degenerate curves with identical signatures.\hfill 2019

Accepted to \textit{Journal of Mathematical Imaging and Vision} and published online:

\url{https://link.springer.com/article/10.1007/s10851-020-01015-x}

\medskip
J. Agudelo, B. Dippold, E. Geiger, I. Klein, I. A. Kogan, A. Kokot,

Curve Reconstruction from Euclidean and Equi-Affine arc-lengths.\hfill 2020

Paper from 2020 summer REU mentoring.

Submitted to \textit{Involve}

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Teaching Experience} \hrulefill}

\medskip
\medskip

\textsf{\textbf{Yale University}}

\medskip
Calculus of Functions of One Variable I   
\hfill Fall 2021, Summer 2022, Fall 2022

Calculus of Functions of One Variable II
\hfill Spring 2022

Calculus of Functions of Several Variables
\hfill Spring 2022

Mathematical Models in the Biosciences I: Calculus Techniques
\hfill Fall 2021, Fall 2022


\medskip
\medskip

\textsf{\textbf{North Carolina State University}}

\medskip
Calculus I - Asynchronous %(65 Students) 
\hfill Fall 2020

Calculus for Life and Management Sciences B %(3 Hybrid Sections of 25 Students)  
\hfill Spring 2020 

Calculus for Life and Management Sciences B %(47 Students) 
\hfill Fall 2019

Introduction to Finite Mathematics %(212 Students) 
\hfill Fall 2018

%\medskip
%\medskip
%\textsf{\textbf{Recitation Leader}}
%
%\medskip 
%Calculus III \hfill Spring 2019
%
%Calculus II \hfill Spring 2018, Spring 2017
%
%Calculus I \hfill Fall 2017
%

\medskip
\medskip
\textsf{\textbf{Other Teaching}}

\medskip
Paradoxes and Infinities (3 week course), \hfill Summer 2019

Johns Hopkins CTY. Seattle, WA 

\medskip
\medskip
\textsf{\textbf{Research Mentorship}}

\medskip
REU Project Mentor, \hfill Summer 2020

Geometric Methods in Computer Vision

NC State. Raleigh, NC

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Awards and Honors}\hrulefill}

\medskip
Project NExT Fellow \hfill 2022

\medskip
Rosenkranz Award for Pedagogical Advancement \hfill 2022

\medskip
NCSU AWM 7-minute Lighting Talk competition co-winner \hfill 2020

\medskip
Thank a Teacher Program, North Carolina State University \hfill 2019

%\medskip
%University Graduate Fellowship, North Carolina State University \hfill 2016

%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{INVITED TALKS}
%
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip


\textsf{\textbf{\Large Conference Presentations} \hrulefill}

\medskip
SIAM Conference on Applied Algebraic Geometry \hfill 2021

Group Actions, Invariants, and Applications Special Session

(Virtual). Speaker.

\medskip
Joint Math Meetings (JMM). \hfill 2021

Geometry in the Mathematics of Data Science Special Session

(Virtual). Speaker.

\medskip
Geometry of curves in time series and shape analysis. \hfill 2020

Max Planck Institute for Mathematics in the Sciences,

Berlin, Germany (Virtual). Invited Speaker.
%Aug 11-14
% put the location so people think I'm international


%\medskip
%Poster presentation, Non-congruent non-degenerate curves with identical signatures, 
%Differential Algebra and Related Topics (DART X).\hfill 2020

%The City University of New York (CUNY), 

%New York, USA. Poster presentation.
%Feb 10-14.

\medskip
Talk - Non-congruent non-degenerate curves with identical signatures at 
Triangle Area Graduate Mathematics Conference (TAGMaC).\hfill 2018

North Carolina State University,  

 Raleigh, USA. Speaker.
%Apr 6.
%
%\medskip
%Tutorial on Multiparameter Persistence, Computation, and Applications.\hfill 2018 
%
%Institute for Mathematics and its Applications, 
%
%Minneapolis, USA.  Attendant.
%Aug 13-15.

%\medskip
%Triangle Area Graduate Mathematics Conference (TAGMaC).  \hfill 2018
%
%UNC-Chapel Hill,
%
%Chapel Hill, USA.  Attendant.
%Apr 28.
%
%\medskip
%Knots in Washington. \hfill 2018
%
%George Washington University,
%
%D.C., USA.  Attendant.
%May 4-6.

%\medskip
%Triangle Area Graduate Mathematics Conference (TAGMaC). \hfill 2017
%
%Duke University,
%
%Durham, USA. Attendant.
%Apr 23.
%%%%%%%%%%%%%%%%%%%
%\bigskip
%\bigskip
%
%\textsf{\textbf{\Large Departmental Talks}\hrulefill}
% Replace this section with Conferences attended
%
%\medskip
%Non-congruent non-degenerate curves with identical signature. \hfill 2020
%
%AWM Lightning Talk Competition. 
%Feb 29.
% put this in awards since I was a winner
%
%\medskip
%Euclidean signature curves and non-congruent planar curves. \hfill 2019
%
%Pure Math Graduate Seminar. 
%%Nov 11.
%
%\medskip
%Bridge trisections of knotted surfaces in 4-manifolds. \hfill 2018
%
%J. Meier, A. Zupan
%
%Trisections Seminar. 
%Mar 28.
% How to properly indicate work being presented is not own?
%
%\medskip
%On the Triangulation of Manifolds and the Haupvermutung. \hfill 2018
%
%R. C. Kirby, L. C. Siebenmann
%
%Vector Bundles Seminar. 
%Mar 1.
% How to properly indicate work being presented is not own?

%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{SERVICE TO PROFESSION}
%
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Programming Languages} \hrulefill}

%\medskip
%Canvas

%\medskip
%Moodle

\medskip
Python

\medskip
MATLAB

\medskip
Maple

\medskip
Mathematica

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Service to Department} \hrulefill}

\medskip

\textsf{\textbf{Yale University}}

\medskip
Member of Climate Committee
\hfill 2022

\medskip
Placement Exam 
\hfill 2022

\medskip
Graduate Student Teaching Mentor \hfill 2021-2022

\bigskip

\textsf{\textbf{North Carolina State University}}

\medskip
Research Presentation for Prospective Graduate Students.
\hfill 2020, 2021

\medskip
Committee Chair on Graduate Instructor Support \& Tools (GIST)
\hfill 2019--2020

%%%%%%%%%%%%%%%%%%%
%\bigskip
%\bigskip

%\textsf{\textbf{\Large Community Outreach} \hrulefill}

%\medskip
%Materials Research Science and Engineering Centers NC-SciFestival. Volunteer. \hfill 2017 

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Extra Training}\hrulefill}

\medskip
MAA Project NExT \hfill 2022

\textit{A year-long professional development program for new or recent Ph.D.s with a focus on improving the teaching and learning of mathematics.}

\medskip
Teaching and Communication Certificate \hfill 2021

\textit{100 hour program designed to increase accessibility, flexibility, and transferability of teaching and communication training for graduate students and postdocs at NC State.}

\medskip
Accessibility in the Classroom

\textit{Online 12 hour course on creating accessible instructional materials.}

\medskip
QPR Institute Suicide Prevention Workshop

\textit{2 hour Question, Persuade, \& Refer suicide prevention workshop}

\medskip
Project SAFE

\textit{Workshop designed to educate participants to understand and address needs of LGBT students}

\medskip
Designing Effective Online Courses Workshop
\textit{12 hour workshop}

%\medskip
%Using the Power of PowerPoint

%\medskip
%Mission Possible: Apps and Other Technology to Engage Learners


%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{REFERENCES}
%
%%%%%%%%%%%%%%%%%%%

\end{document}
