\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
%\usepackage{lipsum}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\fancyfoot[R]{
  \quad \hrule \quad \\
  \textsf{Eric Geiger - Curriculum Vitae \hfill \thepage}
}

\setlength\parindent{0pt}

% Add courses prepared to teach section

\begin{document}
\textsf{\textbf{\LARGE Eric Geiger}}
% Last updated: 2/24/2020 

\bigskip

Department of Mathematics \hfill Cell: (919) 434-7608 

North Carolina State University \hfill E-mail: edgeiger@ncsu.edu

2108 SAS Hall \hfill Website: https://egeig.com 

Box 8205 

Raleigh, North Carolina 27695

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip
\bigskip

\textsf{\textbf{\Large Education} \hrulefill}

\medskip
Ph.D., Mathematics, North Carolina State University \hfill Expected 2021

Advisor: Irina Kogan

\medskip
 M.S., Mathematics, North Carolina State University  \hfill 2018

\medskip
B.S., Mathematics, University of North Carolina at Chapel Hill \hfill 2014

Minor in Religious Studies
        
%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{PROFESSIONAL APPOINTMENTS}
%
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Publications and Preprints} \hrulefill}

\medskip
E. Geiger, I. A. Kogan, Non-congruent non-degenerate curves with identical signatures (preprint).\hfill 2019

Available at \textit{arxiv:1912.09597} 


%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Teaching Experience} \hrulefill}

\medskip
\medskip

\textsf{\textbf{Instructor Of Record}}

\medskip
Calculus for Life and Management Sciences B - Hybrid Section \hfill Spring 2020 

Calculus for Life and Management Sciences B \hfill Fall 2019

Introduction to Finite Mathematics \hfill Fall 2018

\medskip
\medskip
\textsf{\textbf{Recitation Leader}}

\medskip 
Calculus III \hfill Spring 2019

Calculus II \hfill Spring 2018, Spring 2017

Calculus I \hfill Fall 2017

\medskip
\medskip
\textsf{\textbf{Non-University}}

\medskip
Paradoxes and Infinities, \hfill Summer 2019

Johns Hopkins CTY. Seattle, WA 

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Awards and Honors}\hrulefill}

\medskip
Thank a Teacher Program, North Carolina State University \hfill 2019

\medskip
University Graduate Fellowship, North Carolina State University \hfill 2016

%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{INVITED TALKS}
%
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Conference Activity} \hrulefill}

\medskip
Moving Frames and their Modern Applications. \hfill 2020 

Banff International Research Station (BIRS), 

Banff, Canada. Attendant.
%Jul 5-10.

\medskip
%Poster presentation, Non-congruent non-degenerate curves with identical signatures, 
Differential Algebra and Related Topics (DART X).\hfill 2020

The City University of New York (CUNY), 

New York, USA. Poster presentation.
%Feb 10-14.

\medskip
%Talk - Non-congruent non-degenerate curves with identical signatures at 
Triangle Area Graduate Mathematics Conference (TAGMaC).\hfill 2018

North Carolina State University,  

 Raleigh, USA. Speaker.
%Apr 6.

\medskip
Tutorial on Multiparameter Persistence, Computation, and Applications.\hfill 2018 

Institute for Mathematics and its Applications, 

Minneapolis, USA.  Attendant.
%Aug 13-15.

\medskip
Triangle Area Graduate Mathematics Conference (TAGMaC).  \hfill 2018

UNC-Chapel Hill,

Chapel Hill, USA.  Attendant.
%Apr 28.

\medskip
Knots in Washington. \hfill 2018

George Washington University,

D.C., USA.  Attendant.
%May 4-6.

\medskip
Triangle Area Graduate Mathematics Conference (TAGMaC). \hfill 2017

Duke University,

Durham, USA. Attendant.
%Apr 23.
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Departmental Talks}\hrulefill}

\medskip
Non-congruent non-degenerate curves with identical signature. \hfill 2020

AWM Lightning Talk Competition. 
%Feb 29.

\medskip
Euclidean signature curves and non-congruent planar curves. \hfill 2019

Pure Math Graduate Seminar. 
%Nov 11.

\medskip
Bridge trisections of knotted surfaces in 4-manifolds. \hfill 2018

Trisections Seminar. 
%Mar 28.
% How to properly indicate work being presented is not own?

\medskip
On the Triangulation of Manifolds and the Haupvermutung. \hfill 2018

Vector Bundles Seminar. 
%Mar 1.
% How to properly indicate work being presented is not own?

%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{SERVICE TO PROFESSION}
%
%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Service to Department} \hrulefill}

\medskip
Research Presentation for Prospective Graduate Students.

\medskip
Committee Chair on Graduate Instructor Support \& Tools (GIST)

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Community Outreach} \hrulefill}

\medskip
Materials Research Science and Engineering Centers NC-SciFestival. Volunteer. \hfill 2017 

%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

\textsf{\textbf{\Large Extra Training}\hrulefill}

\medskip
Accessibility in the Classroom

\medskip
QPR Institute Suicide Prevention Workshop

\medskip
Project SAFE

\medskip
Using the Power of PowerPoint

\medskip
Mission Possible: Apps and Other Technology to Engage Learners

\medskip
\medskip

\textsf{\textbf{Programming Languages}}

\medskip

Python

MATLAB

Maple


%%%%%%%%%%%%%%%%%%%
%\bigskip
%\hrule
%
%\medskip
%\textbf{REFERENCES}
%
%%%%%%%%%%%%%%%%%%%

\end{document}
